HSC Synthetic Pipeline I: Basic Design and Characterization of HSC Photometric Performance

### 2017-04-15 draft/ms_v2.tex
Song: Organize Susan's edit

\def\redm{\texttt{redMaPPer}}
\def\hscpipe{\texttt{hscPipe}}
\def\synpipe{\texttt{SynPipe}}
\def\cmodel{\texttt{cModel}}
\def\forced{\texttt{forced}}
\def\unforced{\texttt{unforced}}
\def\tract{\texttt{Tract}}
\def\visit{\texttt{Visit}}
\def\tracts{\texttt{Tracts}}
\def\visits{\texttt{Visits}}
\def\galsim{\texttt{G}{\scriptsize \texttt{AL}}\texttt{S}{\scriptsize \texttt{IM}}}
\def\hst{{\textit{HST}}}
\def\s2n{{$\mathrm{S}/\mathrm{N}$}}

@@

    The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band survey 
    using the Hyper Suprime-Cam (HSC) on the Subaru telescope.
    As SSP reaches to detection limit of $i>26.0$ mag in the Wide field, it is 
    challenging to achieve accurate, unbiased, and consistent photometry across all 
    five bands.
    To improve data processing and achieve accurate photometric measurements, we have 
    developed \synpipe{}, a \texttt{Python}-based, flexible framework that interfaces 
    with the HSC data reduction pipeline (\hscpipe{}) to process data from the first 
    public HSC--SSP data release. 
    In the first paper of this series, we explain the design and implementation of 
    \synpipe{}, and use coadd images in two Wide layer \tracts{} with representative 
    seeing conditions to examine the photometric performance of \hscpipe{}.
    We find that uncertainties of HSC \forced{} PSF photometry for stars typically
    range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$
    mag (1\%-7\% accuracy in the $i$-band). 
    For synthetic galaxies based on a single-\ser{} model, uncertainties of the
    forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag 
    to 0.20 mag at $i{\sim} 25.2$ mag.
    Over the color and magnitude ranges used in these \synpipe{} tests, we find that 
    both \forced{} PSF and \cmodel{} photometry provide unbiased color estimates 
    that are robust in different seeing conditions.
    We also notice a few issues in the current \hscpipe{} that are worth keeping
    in mind when using HSC data: 
    1) The degree to which an object is blended with others impacts the photometric 
    accuracy, especially for point sources.
    Highly blended objects tend to have larger photometric uncertainty, systematically
    underestimated flux, and slightly biased color.
    2) A relatively high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
    misclassified as extended objects.
    3) The shape and size estimates for galaxies using \cmodel{} suffer from strong
    biases.

@@

    %% Background
    Wide-field, multi-band imaging surveys have stepped onto the central stage of
    modern astrophysics and cosmology over the past decade.
    They also have a bright future on many current and planned ambitious projects, such as the Large Synoptic Survey Telescope
    (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey
    Telescope
    (WFIRST; \citealt{Dressler2012})\footnote{\url{https://wfirst.gsfc.nasa.gov/}},
    and the \textit{Euclid} project
    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}.
    Among many ongoing efforts, the Subaru Strategic Program
    (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}, which
    uses the Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}) on the prime focus of
    the Subaru telescope, is the most efficient in terms of etendue.
    Together, these surveys will greatly help us test cosmological models, trace the
    evolution of galaxies, study the stellar structure of our Milky Way, and discover
    a large number of interesting transient objects.

    %% Challenges
    Before we can tackle any outstanding scientific questions, we must first learn
    how to handle the huge \susan{quantify? Or is "huge" a common descriptor for data in your field?} amount of data generated by these projects as well as achieve
    accurate photometric measurements of different types of objects.
    Data handling becomes increasingly challenging in the age of modern imaging
    surveys, in part due to variations and effects related to the cameras' charge-coupled devices (CCDs).
    The cameras are often made up of multiple
  CCDs, each with slightly different characteristics, and have
    large fields-of-view (FoV) over not perfectly flat focus planes.
    During  observation, the seeing and background conditions always show spatial
    and temporal variations across the FoV.
    The full-depletion, thick CCDs selected for the cameras enable long exposure times
    and excellent sensitivity in the red-end, but they often have the so-called
    ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that bright
    stars appear larger than they are.
   These variations and effects make accurate astrometric and photometric calibration,
    background subtraction, and point spread function (PSF) modeling intrinsically
    difficult (e.g., \citealt{Schlafly2012}).
    The multi-epoch, multi-band nature of the surveys also complicate
    data reduction because the scientist must pay special attention to
    image stacking, multi-band object detection, and measurement processes.
     Furthermore, as ongoing surveys reach to increasingly deeper surface brightness levels,
    the number of objects, especially faint objects, in a unit area, becomes much higher.
   In addition, it is much more common to observe objects that overlap each other at
    different levels (a phenomenon often referred to as ``blended'').
    These modern imaging survey challenges call for photometric measurement methods that are more powerful and precise than those
    used in previous, shallower surveys.

%% ------------------------------------------------------------------------------------ %%
    %% Reason
    The challenges are not merely technical details; their resolution is crucial
     to achieving the surveys' key scientific goals.
    For instance, weak gravitational lensing (WL; \citealt{Kaiser1993, Bartelmann2001})
    is a powerful tool for measuring the large-scale distribution of dark matter and
    following its evolution.
    However, WL measurements critically depend on the ability to model PSF and measure the
    shape of background galaxies with high precision (e.g., \citealt{Mandelbaum2015}).
    The photometric redshift measurement (e.g., \citealt{Benitez2000, Bolzonella2000,
    Ilbert2009}) is fundamentally important for studying the evolution of galaxies,
    and the ``drop-out'' method is very useful in selecting high-redshift galaxies
    (e.g., \citealt{Steidel1996}).
    However, both of those methods are based on accurate multi-band photometric measurements.
    There are many other examples, but these are sufficient to demonstrate that we need to develop new frameworks
    to oversee the data reduction process of modern imaging surveys.
    Several tools with similar goals have been developed (e.g., \citealt{Chang2015,
    Suchyta2016}) for the Dark Energy Survey (DES; \citealt{DES2005}). \susan{Clarify why you mention the DES tools; e.g., does synpipe build on these tools? Do they demonstrate the effectiveness of developing new frameworks? Why are they insufficient for the HSC survey tasks?}

    %% Organization
  To test the data reduction quality of the HSC--SSP (hereafter referred to
    as the HSC survey) using synthetic objects, we have designed \synpipe{}, a \texttt{Python}-based
    software that
  is a flexible framework with many applications
    that can help future developments of the HSC data reduction pipeline as well as HSC Synthetic Pipeline I.
    Below, we briefly introduce the HSC survey and the current status of
    data reduction (Section \ref{sec:ssp}),  explain  \synpipe{}  design and implementation (Section \ref{sec:synpipe}), and demonstrate \synpipe{} usage via
    straightforward tests (Section \ref{sec:test}) that focus on the general
    photometric quality for both synthetic stars and galaxies
    (Section \ref{sec:result}).
 We then summarize the work and discuss future developments in 
    Section \ref{sec:summary}.

   The  \synpipe{} code, along with basic documents and a few examples, is available
    on GitHub at: \url{https://github.com/dr_guangtou/synpipe}. \susan{Is this URL correct? I got a 404 Page Not Found when I tried it. I think the underscore needs to be replaced with a hyphen: https://github.com/dr-guangtou/synpipe}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of  \synpipe{} basic procedures.
        Grey  boxes indicate the required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects simulated
        images of synthetic objects onto a single-frame image. 
        We show an example CCD image with and without synthetic objects on it
        (highlighted by green circles).
        Red boxes depict the subsequent image coadding and multiband measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py} from \hscpipe{}.
        We show a small piece of coadded image with synthetic objects on it.
        The figure on the right side of the middle row shows the spatial relation
        between \tract{} (outlined by the black dashed lines; each small region
        is a \texttt{Patch}) and all the \visits{} that contribute to it. (Each \visit{} has a  unique color; each small region is the size
        of a CCD.)
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    %% Basic
    Taking advantage of the new prime focus camera on the 8.2 m \susan{Style preference: space between value and m? Hyphenate?} Subaru telescope,
    the ambitious HSC survey consists of three layers: Wide, Deep, and UltraDeep.
    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broad bands
    ($grizy$; Kawanomoto\etal in prep.).
    The Deep (4 separated fields; ${\sim}27$ deg$^2$) and UltraDeep (2 separated
    fields; ${\sim}3.5$ deg$^2$) layers will use a few additional narrow-band filters
    and employ a slightly different surveying strategy.
     Strauss\etal (in prep.) describes the HSC survey in more detail, and identifies the HSC collaborators.

@@

   In February 2017, the HSC collaboration  released the first 1.7 years of data to the public (DR1;
    \citealt{HSCDR1})\footnote{\url{https://hsc_release.mtk.nao.ac.jp }}.\susan{URL is incorrect. Replace underscore with hyphen and add /doc: https://hsc-release.mtk.nao.ac.jp/doc/}
    For our work, we  focused on data from the Wide layer and the related major scientific goals, which include
    WL cosmology, galaxy evolution since $z{\sim}1$, and studies of galaxy clusters.
    The current Wide layer includes ${\sim}108$ deg$^2$ of sky isolated in
    6 different regions (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
    \footnote{A small AEGIS field is also observed for calibration purposes.}.
    Except for the HECTOMAP field, the regions are all close to the equator. 
        In the Wide layer, the $g$ and $r$ bands have 10 mins of exposure broken into 4
    dithers\footnote{Large, ${\sim}1/3$ of the FoV dither pattern is used to ensure
    uniform coverage.}; for the remaining 3 bands, 20 mins of exposure time and 6 dithers are
    used\footnote{Several 30 s exposures are taken to improve the dynamic range.}.
    The survey prioritizes the observations so that the $i$-band can have excellent
    seeing conditions to help make accurate WL shape measurements.
    The current Wide layer has impressive median seeing with FWHM${\sim}0.6$\asec{},
    and has a $i{\sim} 26.4$ mag $5\sigma$ point source detection limit. 
    \citealt{HSCDR1} provides details on the first data release and data status.
 .
%% ------------------------------------------------------------------------------------ %%

@@

    The HSC survey data are \susan{Style preference: data plural or singular? Later you use plural, and that's my preference, so I've changed the verb here.} currently reduced by \hscpipe{} \texttt{v4.0.5}, a
    version of the LSST reduction pipeline (\citealt{Ivezic2008, Axelrod2010,
    Juric2015}), which is described in detail in Bosch\etal (in prep.).
    Since \synpipe{} is intrinsically connected to the complex data reduction
    processes in \hscpipe{},  we briefly introduce the main steps below, along with
    a few key HSC/LSST terms.

@@

        \item \textbf{Multi-\texttt{Visit~}Processing}:
            After single-\texttt{Visit~} processing, \hscpipe{}  warps and mosaics the reduced CCD images into
            much deeper \texttt{coadded} images while improving the astrometric and
            photometric calibrations via processes similar to the \"{u}ber-calibration
            in the Sloan Digital Sky Survey (SDSS) \citep{Padmanabhan2008}.
            \textbf{\synpipe{} will use these improved calibrations.}
            \hscpipe{} organizes these \texttt{coadded} images into equiareal \susan{or equal-area but not equi-area}
            rectangular regions, or \tracts{}, which are predefined as iso-latitude tessellations.
            One \tract{} covers approximately $1.7\times 1.7$ deg$^2$ of
            sky, and adjacent \tracts{} overlap each other by ${\sim}1$\amin{}.
            Each \tract{} is further divided into $9\times9$ \texttt{Patches}.
            A \texttt{Patch} is a $4200\times4200$ pixels rectangular region, and
            adjacent \texttt{Patches} overlap each other by 100 pixels.
            \textbf{The \tract{} and \texttt{Patch} are basic units to deal
            with HSC \texttt{coadded} images and \synpipe{} tests.}

        \item \textbf{Multi-band Measurements}:
            To achieve consistent photometry across all filters, \hscpipe{} first
            detects and deblends objects on \texttt{coadded} images in each band
            independently (the \unforced{} measurements).
            The collection of above-threshold pixels for each object is referred to as
          a  \texttt{footprint}.
           \hscpipe{} merges the \texttt{footprints} and flux peaks in the different
            bands and then selects a reference band for each object based on its $S/N$ in
            each band (usually it is the $i$-band).
            With the centroids, shape, and other non-amplitude parameters fixed at the
            reference values, \hscpipe{} performs \forced{} photometry, which is
            optimized to generate accurate colors.

        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain a variety of photometric
            information (see \citealt{HSCDR1} for details).
            \textbf{Here, we focus on the \forced{} \texttt{psf} and \cmodel{}
            photometry.}
            \texttt{psf} photometry should provide the most appropriate magnitudes and
            colors for point sources.
            Improved over the SDSS version (\citealt{Lupton2001, Abazajian2004}),
            the HSC \cmodel{}{} algorithm (described in Bosch\etal, in prep.) fits 
           each object's flux distribution using a combination of the de Vaucouleur
            profile and an exponential component that takes the PSF convolution into account.
            \cmodel{} is designed to yield accurate colors for galaxies.
            In addition, the star--galaxy separation task is performed based on the
            difference between the \texttt{psf} and \cmodel{}{} magnitudes.

@@

     \hscpipe{} is a complex data reduction pipeline that still faces many challenges
    and is under active development. 
    Unlike most photometric pipelines on the market, it involves high-level reduction
    processes that produce not only deep \texttt{coadded} images but also a series of
    science-ready catalogs.
    To faithfully test \hscpipe{} and the related data products, we have designed an approach that ensures
    \synpipe{} satisfies a few basic standards:

@@

        \item \textbf{Realistic Images}:
            Instead of using the fully generative approach to simulate full HSC-like
            images from the ground up (e.g., \citealt{Chang2015}), \synpipe{} injects
            synthetic objects into the observed image so that all the realistic
            features of the real data (e.g., blended objects; proximity to bright
            objects, bleeding trails, other optical artifacts \susan{It's redundant to use etc. (or et al, which is incorrect here) with e.g.}) can be included
            in the test.
            The impact of these features can be important to any topic (e.g., WL analysis; stellar mass function of galaxies) that cares
            about the selection function and completeness of samples.
            In \synpipe{}, point source is simulated using the HSC PSF model,
            and a realistic galaxy model is created by the modular galaxy image
            simulation toolkit, \galsim{} (\citealt{Rowe2015})
            \footnote{\url{https://github.com/GalSim_developers/GalSim}} \susan{I got 404 Page Not Found when I tested the URL. Change underscore to hyphen: https://github.com/GalSim-developers/GalSim}.

        \item \textbf{Authentic Data Processing}:
            To follow the data reduction process as closely as possible, we choose to
            start from the single-\visit{} images instead of directly putting
            synthetic objects on the final \texttt{coadded} images
            (e.g., \citealt{Suchyta2016}).
            Through this approach, subtle effects like seeing differences among
            \visits{} and small errors in astrometric calibration can be taken
            into account.
            Every synthetic object will experience all the steps we would use for any real object: detection,
            deblending, stacking, and measurement.
            This can be important for challenging tasks like the WL measurements
            or the detection of high-$z$ galaxies.
            The only downside of this choice is that it will certainly slow down the
            test for \texttt{coadded} images because in this approach we need to inject synthetic objects
            into all the \visits{} that contribute to a \tract{}.

@@

        \item \textbf{Information about the data} includes the
            location of the HSC images and a list of \visits{} for the
            test.
            To test the \texttt{coadded} images, \synpipe{} can help the user identify
            all the \visits{} that contribute to one \tract{} in any given
            band.
            \synpipe{} also provides tools to create an optional bad-pixel mask (e.g., bright
            object, bleeding trail) for a specific \tract{} so that the user can avoid
            putting synthetic objects on problematic regions.

        \item \textbf{Input catalog} in  \texttt{FITS} format contains the necessary
            information, including the coordinate, magnitude, and other model parameters.  susan{Define FITS at first use? Flexible Image Transport System (FITS); I didn't change it because I didn't want to jeopardize the LaTeX coding on FITS.} 
            For any given sample of synthetic objects, \synpipe{} can help the user randomly
            distribute the objects in a selected rectangular region with the desired 
            density.
            If necessary,  \synpipe{}  can reduce overlaps of synthetic objects by setting a minimum distance between any two of them. \susan{Unclear: does the user set the minimum distance, or does synpipe? If the user, change to If necessary,  the user can reduce overlaps of synthetic objects by setting a minimum distance between any two of them. } 
            \synpipe{} can also help put synthetic objects on an evenly separated
            coordinate grid, which is very useful for certain tests
            (e.g., Murata\etal in prep.).

@@

    The newly generated single-\visit{} images have the same format and data
    structure as the real HSC data; therefore, \synpipe{} can directly feed them
    to the other \hscpipe{} steps.
    The \texttt{stack.py} step takes the improved astrometric and photometric
    calibrations for each \visit{} from the original reduction and creates
    \texttt{coadded} images with synthetic objects on them.
    Then the \texttt{multiBand.py} step processes these \texttt{coadded} images and
    provides standard multi-band measurements in FITS catalogs that are grouped by
    \texttt{Patch} ID.

>>>>

\def\redm{\texttt{redMaPPer}}
\def\hscpipe{\texttt{hscPipe}}
\def\synpipe{\texttt{SynPipe}}
\def\cmodel{\texttt{cModel}}
\def\forced{\texttt{forced}}
\def\coadd{\texttt{coadd}}
\def\unforced{\texttt{unforced}}
\def\tract{\texttt{Tract}}
\def\visit{\texttt{Visit}}
\def\tracts{\texttt{Tracts}}
\def\visits{\texttt{Visits}}
\def\galsim{\texttt{G}{\scriptsize \texttt{AL}}\texttt{S}{\scriptsize \texttt{IM}}}
\def\hst{{\textit{HST}}}
\def\s2n{{$\mathrm{S}/\mathrm{N}$}}

@@

    The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band survey 
    using the Hyper Suprime-Cam (HSC) on the Subaru telescope.
    As SSP reaches to detection limit of $i>26.0$ mag in the Wide field, it is 
    challenging to achieve accurate, unbiased, and consistent photometry across all 
    five bands.
    To improve data processing and achieve accurate photometric measurements, we have 
    developed \synpipe{}, a \texttt{Python}-based, flexible framework that interfaces 
    with the HSC data reduction pipeline (\hscpipe{}) to process data from the first 
    public HSC--SSP data release. 
    In the first paper of this series, we explain the design and implementation of 
    \synpipe{}, and use \coadd{} images in two Wide layer \tracts{} with representative 
    seeing conditions to examine the photometric performance of \hscpipe{}.
    We find that uncertainties of HSC \forced{} PSF photometry for stars typically
    range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$
    mag (1\%-7\% accuracy in the $i$-band). 
    For synthetic galaxies based on a single-\ser{} model, uncertainties of the
    forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag 
    to 0.20 mag at $i{\sim} 25.2$ mag.
    Over the color and magnitude ranges used in these \synpipe{} tests, we find that 
    both \forced{} PSF and \cmodel{} photometry provide unbiased color estimates 
    that are robust in different seeing conditions.
    We also notice a few issues in the current \hscpipe{} that are worth keeping
    in mind when using HSC data: 
    1) The degree to which an object is blended with others impacts the photometric 
    accuracy, especially for point sources.
    Highly blended objects tend to have larger photometric uncertainty, systematically
    underestimated flux, and slightly biased color.
    2) A relatively high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
    misclassified as extended objects.
    3) The shape and size estimates for galaxies using \cmodel{} suffer from strong
    biases.

@@

    %% Background
    Wide-field, multi-band imaging surveys have stepped onto the central stage of
    modern astrophysics and cosmology over the past decade.
    They also have a bright future on many current and planned ambitious projects, 
    such as the Large Synoptic Survey Telescope
    (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey
    Telescope
    (WFIRST; \citealt{Dressler2012})\footnote{\url{https://wfirst.gsfc.nasa.gov/}},
    and the \textit{Euclid} project
    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}.
    Among many ongoing efforts, the Subaru Strategic Program
    (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}, which
    uses the Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}) on the prime focus of
    the Subaru telescope, is the most efficient in terms of 
    etendue\footnote{The collecting area multiplied by the field of view.}.
    Together, these surveys will greatly help us test cosmological models, trace the
    evolution of galaxies, study the stellar structure of our Milky Way, and discover
    a large number of interesting transient objects.

    %% Challenges
    Before we can tackle any outstanding scientific questions, we must first learn
    how to handle the huge amount of data\footnote{Right now, SSP has accumulated 
    ${\sim}300$ TB of data products.} generated by these projects as well as achieve
    accurate photometric measurements of different types of objects.
    Data handling becomes increasingly challenging in the age of modern imaging
    surveys, in part due to variations and effects related to the cameras' 
    charge-coupled devices (CCDs).
    The cameras are often made up of multiple CCDs, each with slightly different 
    characteristics, and have large fields-of-view (FoV) over not perfectly flat 
    focus planes.
    During observation, the seeing and background conditions always show spatial
    and temporal variations across the FoV.
    The full-depletion, thick CCDs selected for the cameras enable long exposure 
    times and excellent sensitivity in the red-end, but they often suffer from the 
    so-called ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that 
    brighter stars appear larger than they are.
    These variations and effects make accurate astrometric and photometric calibration,
    background subtraction, and point spread function (PSF) modeling intrinsically
    difficult (e.g., \citealt{Schlafly2012}).
    The multi-epoch, multi-band nature of the surveys also complicate data reduction 
    because the scientist must pay special attention to image stacking, multi-band 
    object detection, and measurement processes.
    Furthermore, as ongoing surveys reach to increasingly deeper detection limit 
    (e.g SSP Wide reaches to $5\ \sigma$ detection limit of point source of 
    ${\sim}26.4$ mag), the number of objects in a unit area, especially faint objects,
    becomes much higher. 
    In addition, it is much more common to observe objects that overlap each other at
    different levels (a phenomenon often referred to as ``blended'').
    These modern imaging survey challenges call for photometric measurement methods 
    that are more powerful and precise than those used in previous, shallower surveys.

%% ------------------------------------------------------------------------------------ %%
    %% Reason
    The challenges are not merely technical details; their resolution is crucial
    to achieving the surveys' key scientific goals.
    For instance, weak gravitational lensing (WL; \citealt{Kaiser1993, Bartelmann2001})
    is a powerful tool for measuring the large-scale distribution of dark matter and
    following its evolution.
    However, WL measurements critically depend on the ability to model PSF and measure 
    the shape of background galaxies with high precision 
    (e.g., \citealt{Mandelbaum2015}).
    The photometric redshift measurement (e.g., \citealt{Benitez2000, Bolzonella2000,
    Ilbert2009}) is fundamentally important for studying the evolution of galaxies,
    and the ``drop-out'' method is very useful in selecting high-redshift galaxies
    (e.g., \citealt{Steidel1996}).
    However, both of those methods are based on accurate multi-band photometric 
    measurements.
    There are many other examples, but these are sufficient to demonstrate that we 
    need to develop new frameworks to oversee the data reduction process of modern 
    imaging surveys.
    Several tools with similar goals have been developed (e.g., \citealt{Chang2015,
    Suchyta2016}) for the Dark Energy Survey (DES; \citealt{DES2005}). 
    As for the HSC--SSP (hereafter referred to as the HSC survey), the higher quality 
    images and more complex \hscpipe{} also require more carefully designed tool to 
    test them.

    %% Organization
    Here, we present \synpipe{}, a \texttt{Python}-based software that is a flexible 
    framework with many applications that can help future developments of the HSC data 
    reduction pipeline (\hscpipe{}).
    Below, we briefly introduce the HSC survey and the current status of data 
    reduction (Section \ref{sec:ssp}), explain \synpipe{} design and implementation 
    (Section \ref{sec:synpipe}), and demonstrate \synpipe{} usage via straightforward 
    tests (Section \ref{sec:test}) that focus on the general photometric quality for 
    both synthetic stars and galaxies (Section \ref{sec:result}).
    We then summarize the work and discuss future developments in 
    Section \ref{sec:summary}.

    The \synpipe{} code, along with basic documents and a few examples, is available
    on GitHub at: \texttt{https://github.com/dr-guangtou/synpipe}.
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of \synpipe{} basic procedures.
        Grey boxes indicate the required inputs at different stages.
        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects 
        simulated images of synthetic objects onto a single-frame image. 
        We show an example CCD image with and without synthetic objects on it
        (highlighted by green circles).
        Red boxes depict the subsequent image coadding and multiband measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py} from \hscpipe{}.
        We show a small piece of \coadd{} image with synthetic objects on it.
        The figure on the right side of the middle row shows the spatial relation
        between \tract{} (outlined by the black dashed lines; each small region
        is a \texttt{Patch}) and all the \visits{} that contribute to it. 
        (Each \visit{} has a  unique color; each small region is the size of a CCD.)
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    %% Basic
    Taking advantage of the new prime focus camera on the 8.2--m Subaru telescope,
    the ambitious HSC survey consists of three layers: Wide, Deep, and UltraDeep.
    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broad bands
    ($grizy$; Kawanomoto\etal in prep.).
    The Deep (4 separated fields; ${\sim}27$ deg$^2$) and UltraDeep (2 separated
    fields; ${\sim}3.5$ deg$^2$) layers will use a few additional narrow-band filters
    and employ a slightly different surveying strategy.
    Strauss\etal (in prep.) describes the HSC survey in more detail, and identifies the 
    HSC collaborators.

@@

    In February 2017, the HSC collaboration released the first 1.7 years of data to 
    the public (DR1; 
    \citealt{HSCDR1})\footnote{\texttt{https://hsc-release.mtk.nao.ac.jp }}.
    For our work, we focused on data from the Wide layer as they relate to key 
    scientific goals of HSC survey, which include WL cosmology, galaxy evolution 
    since $z{\sim}1$, and studies of galaxy clusters.
    The current Wide layer includes ${\sim}108$ deg$^2$ of sky isolated in
    6 different regions (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
    \footnote{A small AEGIS field is also observed for calibration purposes.}.
    Except for the HECTOMAP field, the regions are all close to the equator. 
    In the Wide layer, the $g$ and $r$ bands have 10 mins of exposure broken into 4
    dithers\footnote{Large, ${\sim}1/3$ of the FoV dither pattern is used to ensure
    uniform coverage.}; for the remaining 3 bands, 20 mins of exposure time and 6 
    dithers are used\footnote{Several 30 s exposures are taken to improve the 
    dynamic range.}.
    The survey prioritizes the observations so that the $i$-band can have excellent
    seeing conditions to help make accurate WL shape measurements.
    The current Wide layer has impressive median seeing with FWHM${\sim}0.6$\asec{},
    and has a $i{\sim} 26.4$ mag $5\sigma$ point source detection limit. 
    \citealt{HSCDR1} provides details on the first data release and data status.

@@

    The HSC survey data are currently reduced by \hscpipe{} \texttt{v4.0.5}, a
    version of the LSST reduction pipeline (\citealt{Ivezic2008, Axelrod2010,
    Juric2015}), which is described in detail in Bosch\etal (in prep.).
    Since \synpipe{} is intrinsically connected to the complex data reduction
    processes in \hscpipe{}, we briefly introduce the main steps below, along with
    a few key HSC/LSST terms.

@@

        \item \textbf{Multi-\visit{} Processing}:
            After single-\visit{} processing, \hscpipe{} warps and mosaics the 
            reduced CCD images into much deeper \coadd{} images while improving
            the astrometric and photometric calibrations via processes similar to 
            the \"{u}ber-calibration in the Sloan Digital Sky Survey (SDSS) 
            \citep{Padmanabhan2008}.
            \textbf{\synpipe{} will use these improved calibrations.}
            \hscpipe{} organizes these \coadd{} images into equiareal rectangular 
            regions, or \tracts{}, which are predefined as iso-latitude tessellations.
            One \tract{} covers approximately $1.7\times 1.7$ deg$^2$ of sky, and 
            adjacent \tracts{} overlap each other by ${\sim}1$\amin{}.
            Each \tract{} is further divided into $9\times9$ \texttt{Patches}.
            A \texttt{Patch} is a $4200\times4200$ pixels rectangular region, and
            adjacent \texttt{Patches} overlap each other by 100 pixels.
            \textbf{The \tract{} and \texttt{Patch} are basic units to deal
            with HSC \coadd{} images and \synpipe{} tests.}

        \item \textbf{Multi-band Measurements}:
            To achieve consistent photometry across all filters, \hscpipe{} first
            detects and deblends objects on \coadd{} images in each band
            independently (the \unforced{} measurements).
            The collection of above-threshold pixels for each object is referred to as
            a \texttt{footprint}.
            \hscpipe{} merges the \texttt{footprints} and flux peaks in the different
            bands and then selects a reference band for each object based on its $S/N$ 
            in each band (usually it is the $i$-band).
            With the centroids, shape, and other non-amplitude parameters fixed at the
            reference values, \hscpipe{} performs \forced{} photometry, which is
            optimized to generate accurate colors.

        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain a variety of 
            photometric information (see \citealt{HSCDR1} for details).
            \textbf{Here, we focus on the \forced{} \texttt{psf} and \cmodel{}
            photometry.}
            \texttt{psf} photometry should provide the most appropriate magnitudes and
            colors for point sources.
            Improved over the SDSS version (\citealt{Lupton2001, Abazajian2004}),
            the HSC \cmodel{} algorithm (described in Bosch\etal, in prep.) fits 
            each object's flux distribution using a combination of the de Vaucouleur
            profile and an exponential component that takes the PSF convolution 
            into account.
            \cmodel{} is designed to yield accurate colors for galaxies.
            In addition, the star--galaxy classification task is performed based on 
            the difference between the \texttt{psf} and \cmodel{}{} magnitudes.

@@

    \hscpipe{} is a complex data reduction pipeline that still faces many challenges
    and is under active development. 
    Unlike most photometric pipelines on the market, it involves high-level reduction
    processes that produce not only deep \coadd{} images but also a series of
    science-ready catalogs.
    To faithfully test \hscpipe{} and the related data products, we have designed an 
    approach that ensures \synpipe{} satisfies a few basic standards:

@@

        \item \textbf{Realistic Images}:
            Instead of using the fully generative approach to simulate full HSC-like
            images from the ground up (e.g., \citealt{Chang2015}), \synpipe{} injects
            synthetic objects into the observed image so that all the realistic
            features of the real data (e.g., blended objects; proximity to bright
            objects, bleeding trails, other optical artifacts can be included in the 
            test.
            The impact of these features can be important to any topic (e.g., WL 
            analysis; stellar mass function of galaxies) that cares about the selection 
            function and completeness of samples.
            In \synpipe{}, point source is simulated using the HSC PSF model,
            and a realistic galaxy model is created by the modular galaxy image
            simulation toolkit, \galsim{} (\citealt{Rowe2015})
            \footnote{\texttt{https://github.com/GalSim-developers/GalSim}}.

        \item \textbf{Authentic Data Processing}:
            To follow the data reduction process as realistic as possible, we choose to
            start from the single-\visit{} images instead of directly putting synthetic 
            objects on the final \coadd{} images (e.g., \citealt{Suchyta2016}).
            Through this approach, subtle effects like seeing differences among
            \visits{} and small errors in astrometric calibration can be taken
            into account.
            Every synthetic object will experience all the steps we would use for any 
            real object: detection, deblending, stacking, and measurement.
            This can be important for challenging tasks like the WL measurements
            or the detection of high-$z$ galaxies.
            The only downside of this choice is that it will certainly slow down the
            test for \coadd{} images because in this approach we need to inject 
            synthetic objects into all the \visits{} that contribute to a \tract{}.

@@

        \item \textbf{Information about the data}
            includes the location of the HSC images and a list of \visits{} for 
            the test.
            To test the \coadd{} images, \synpipe{} can help the user identify
            all the \visits{} that contribute to one \tract{} in any given
            band.
            \synpipe{} also provides tools to create an optional bad-pixel mask 
            (e.g., bright object, bleeding trail) for a specific \tract{} so that 
            the user can avoid putting synthetic objects on problematic regions.

        \item \textbf{Input catalog} in \texttt{FITS} (Flexible Image Transport System)
            format contains the necessary information, including the coordinate, 
            magnitude, and other model parameters.  
            For any given sample of synthetic objects, \synpipe{} can help the user 
            randomly distribute the objects in a selected rectangular region with the
            desired density.
            If necessary, the user can reduce overlaps of synthetic objects by setting 
            a minimum distance between any two of them. 
            \synpipe{} can also help put synthetic objects on an evenly separated
            coordinate grid, which is very useful for certain tests
            (e.g., Murata\etal in prep.).

@@

    The newly generated single-\visit{} images have the same format and data
    structure as the real HSC data; therefore, \synpipe{} can directly feed them
    to the other \hscpipe{} steps.
    The \texttt{stack.py} step takes the improved astrometric and photometric
    calibrations for each \visit{} from the original reduction and creates
    \coadd{}  images with synthetic objects on them.
    Then the \texttt{multiBand.py} step processes these \coadd{}  images and
    provides standard multi-band measurements in FITS catalogs that are grouped by
    \texttt{Patch} ID.

    Using the infrastructures provided by \hscpipe{}, the user can easily perform the 
    above processes in parallel, and the overall efficiency of \synpipe{} is similar to 
    the real data reduction process.
    The processes also generate the same amount of images and catalog data as the 
    original data reduction process.
